---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# kwb.default

This package provides functions that allow you to change the default behaviour of your user defined functions. 

## Installation

You can install the latest development version of the package `kwb.default` from github with

```R
# install.packages("devtools")
devtools::install_github("kwb-r/kwb.default")
```

## Usage

First of all, you need to load the package:

```{r}
library(kwb.default)
```

### Setting default values

Instead of setting constant values in your function's definition, you can use calls to `getDefault()` that look up the current default values for the function's arguments when you call the function without these arguments being set. So, instead of defining a function `hello1()` with constant default values `"Mona"` and `"Lisa"` for the formal arguments `firstName` and `lastName`, respectively:

```{r}
hello1 <- function
(
  firstName = "Mona", 
  lastName = "Lisa"
) 
{
  cat(paste0("Hello ", firstName, " ", lastName, "!\n"))
}
```

you define the function by assigning calls to `getDefault()` as default values, like this:

```{r}
hello2 <- function
(
  firstName = getDefault("hello2", "firstName"),
  lastName = getDefault("hello2", "lastName")
) 
{
  cat(paste0("Hello ", firstName, " ", lastName, "!\n"))
}
```

You then set the default values separately with `setDefault()`:

```{r}
setDefault("hello2", firstName = "Mona", lastName = "Lisa")
```

Both functions now behave in the same way:

```{r}
hello1()
hello2()
```

However, for `hello2()` we can easily change the default values without having to update the function's definition, just by calling `setDefault()` again:

```{r}
setDefault("hello2", firstName = "Don", lastName = "Quichote")
```

If you call the function now without arguments, the new defaults are used:

```{r}
hello2()
```

Note that `setDefault()` will raise an error if the function specified does not exist

```{r, error = TRUE}
tryCatch(setDefault("hello", firstName = "Peter"))
```

### Getting default values

To read the current settings of default values, use `getDefault()`:

```{r}
getDefault("hello2", "firstName")
getDefault("hello2", "lastName")
```
